Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-28 journal/article.tex
T: Change leaders

@@

@@

>>>>

* Kotter: Having a ``guiding team'' for change

@@

\subsubsection{How change was lead}

A significant change effort requires entities in the organization who take
leadership in the change.

Change was lead in X ways.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Type of leading change         &  Described in  \\
        \midrule
        Agile task group foor coordinating change   &
                P4, P18, P21, P23, P25, P30, P40, P41,
                P43, P45, P48, P49, P50  \\
        \bottomrule
    \end{tabular}
    \caption{Which entities were leading change in the agile transformation}
    \label{table:transformation_leadership}
\end{table}

% Agile task force

Many organizations formed an agile task force or similar entity for coordinating
and leading the change. It was typical that in the beginning of the
transformation, or when it had been acknowledged that the old model had
problems, a work group was founded for coordinating the changes to be done. The
change team usually consisted of management personnel [P43, P50], and was
reinforced with external agile consultants [P18, P21, P25, P30]. Some cases
highlighted that the team had a cross organizational staff who were familiar
with the varying functions that would be affected by changes [P4, P21, P41,
P48]. It was important that theere was a group of people who were strongly
committed to making a change happen [P43].

The tasks of the change team included first finding an alternative delivery
method to solve problems in the old model [P21, P30]. During the transformation
the team stimulated agile adoption in the organization [P18, P45, P49]. Examples
on their tasks were informing people on the agile model [P4], educating and
coaching [P45, P48, P49], creating an agile cookbook [P23], and organizing
presentations and workshops [P25, P41]. The change team also assessed the
success of transformed teams, and worked for repeating their success across the
organization [P40, P41].
% The team was also empowered to remove the impediments they discovered [P50].

@@

* How do transformations fit within Kotter's 8 step process?
